\documentclass{article}
\usepackage{times} % Required for inserting images

\begin{document}

\begin{abstract}
        
\end{abstract}


\noindent We take this opportunity to express our deepest \&\ sincere gratitude to our Project Supervisor Prof. Dr. Subarna Shakya, Department of Electronics and Computer Engineering, Institute of Engineering, Pulchowk, for his insightful advice, motivating suggestions, invaluable guidance, help, and support in the successful completion of this project, and also for his/her constant encouragement and advice throughout our Bachelor's
program.\par
\vspace{5pt}
\noindent We express our deep gratitude to Er. Ajaya Shrestha, Head of the Department of Electronics and Computer Engineering, Er. Bikash Acharya, Deputy Head, Department Of Electronics and Computer Engineering, Er. Laxmi Prasad Bhatt, Academic Project Coordinator, Department Of Electronics and Computer Engineering for their regular support, cooperation, and coordination.\par 
\vspace{5pt}
\noindent The in-time facilities provided by the department throughout the Bachelor's program are also equally acknowledgeable.\par 
\vspace{5pt}
\noindent We would like to convey our thanks to the teaching and non-teaching staff of the Department of Electronics and Communication and Computer Engineering, ACEM for their invaluable help and support throughout the period of Bachelor’s Degree. We are also grateful to all our classmates for their help, encouragement, and invaluable suggestions.\par
\vspace{5pt}

\noindent Finally, yet more importantly, I would like to express our deep appreciation to our grandparents, parents, and siblings for their perpetual support and encouragement throughout
the Bachelor’s degree period.\par
\vspace{20pt}
\noindent Sugam Sen Sinjali
\end{document}
